Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-12 submission/abstract_file.tex
fix typos after full read

In many practical applications, one works with deep neural network (DNN) models trained by someone else.
For such \emph{pretrained models}, one typically does not have access to training data or test data.
Moreover, one does not know many details about the model, such as the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, can one say anything about the expected performance or quality of the models?
Here, we present and evaluate empirical quality metrics for pretrained DNN models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
%%The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
%The most promising are norm-based metrics
% (such as those used to provide capacity control in traditional statistical learning theory) 
%and metrics based on fitting eigenvalue distributions to truncated power law (PL) distributions 
%(which derive from statistical mechanics, in particular the recently-developed Theory of Heavy-Tailed Self Regularization, and which characterize the strength of correlations in a DNN). 
%
Using the open-source \emph{WeightWatcher} tool, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision (CV) and natural language processing (NLP).
We examine both familiar norm-based capacity control metrics (Frobenius and Spectral norms) as well as newer Power-Law (PL) based metrics (including fitted PL exponents, $\alpha$, and the Weighted Alpha metric, $\hat{\alpha}$), from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
We also introduce the $\alpha$-Shatten Norm metric.
We find that norm-based metrics correlate well with reported test accuracies for well-trained models across nearly all CV architecture series.
On the other hand, we find that norm-based metrics can not distinguish ``good-versus-bad'' models---which, arguably is the point of needing quality metrics.  
Indeed, they may give spurious results.
We also find that PL-based metrics do much better---quantitatively better at discriminating among a series of ``good-better-best'' models, and qualitatively better at discriminating ``good-versus-bad'' models.
PL-based metrics can also be used to characterize fine-scale properties of these models, and we introduce the layer-wise \emph{Correlation Flow} as new quality assesment.
We show how poorly-trained (and/or poorly fine-tuned) models may exhbit both \emph{Scale Collapse} and unsually large PL exponents, $\alpha\gg 6$, in particular for recent NLP models.
Our techniques, as implemented in the \emph{WeightWatcher} tool, can be used to identify when a pretrained DNN has problems that can not be detected simply by examining training/test accuracies.

>>>>

In many practical applications, one works with deep neural network (DNN) models trained by someone else.
For such \emph{pretrained models}, one typically does not have access to training data or test data.
Moreover, one does not know many details about the model, such as the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, can one say anything about the expected performance or quality of the models?
Here, we present and evaluate empirical quality metrics for pretrained DNN models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
%%The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
%The most promising are norm-based metrics
% (such as those used to provide capacity control in traditional statistical learning theory) 
%and metrics based on fitting eigenvalue distributions to truncated power law (PL) distributions 
%(which derive from statistical mechanics, in particular the recently-developed Theory of Heavy-Tailed Self Regularization, and which characterize the strength of correlations in a DNN). 
%
Using the open-source \emph{WeightWatcher} tool, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision (CV) and natural language processing (NLP).
We examine both familiar norm-based capacity control metrics (Frobenius and Spectral norms) as well as newer Power Law (PL) based metrics (including fitted PL exponents, $\alpha$, and the Weighted Alpha metric, $\hat{\alpha}$), from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
We also introduce the $\alpha$-Shatten Norm metric.
We find that norm-based metrics correlate well with reported test accuracies for well-trained models across nearly all CV architecture series.
On the other hand, we find that norm-based metrics can not distinguish ``good-versus-bad'' models---which, arguably is the point of needing quality metrics.  
Indeed, they may give spurious results.
We also find that PL-based metrics do much better---quantitatively better at discriminating among a series of ``good-better-best'' models, and qualitatively better at discriminating ``good-versus-bad'' models.
PL-based metrics can also be used to characterize fine-scale properties of these models, and we introduce the layer-wise \emph{Correlation Flow} as new quality assesment.
We show how poorly-trained (and/or poorly fine-tuned) models may exhbit both \emph{Scale Collapse} and unsually large PL exponents, $\alpha\gg 6$, in particular for recent NLP models.
Our techniques, as implemented in the \emph{WeightWatcher} tool, can be used to identify when a pretrained DNN has problems that can not be detected simply by examining training/test accuracies.

### 2020-02-12 submission/all_models.tex
fix typos after full read

In this section, we summarize results from a large-scale analysis of hundreds of CV models, including models developed for image 
classification, segmentation, and a range of related tasks.  
Our aim is to complement the detailed results from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} by providing broader conclusions. % about norm-based and PL-based metrics.
The models we consider have been pretrained on nine datasets, shown in Table~\ref{table:datasets}.
%including ImageNet-1K, and CIFAR-10, CIFAR-100, Street View House Numbers (SVHN), Caltech-UCSD Birds-200-2011 (CUB-200-2011), Pascal VOC2012, ADE20K, Cityscapes, and Common Objects in Context (COCO). 
%%The pretrained models and their accuracy metrics are summarized in the osmr github~\cite{charles-add-link}.
We provide full details about how to reproduce these results in Appendix~\ref{sxn:appendix}.

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
Series        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean) & 0.63 &  0.55 & \textbf{0.64} & \textbf{0.64} \\
$R^{2}$ (std)  & 0.34 &  0.36 & \textbf{0.29} &          0.30 \\
\hline
$MSE$ (mean)   & 4.54 &  9.62 &          3.14 & \textbf{2.92} \\
$MSE$ (std)    & 8.69 & 23.06 &          5.14 & \textbf{5.00} \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average Log Norm and Weighted Alpha metrics across 5 CV datasets, 17 architectures, covering 168 (out of 309) different pretrained DNNs.  
         We include regressions only for architectures with 4 or more data points, and which are postively correlated with test error.
         These results can be readily reproduced using the Google Colab notebooks (see Appendix~\ref{sxn:appendix}). 
        }
\label{table:results}
\end{table}

>>>>

In this section, we summarize results from a large-scale analysis of hundreds of CV models, including models developed for image 
classification, segmentation, and a range of related tasks.  
Our aim is to complement the detailed results from Sections~\ref{sxn:cv} and~\ref{sxn:nlp} by providing broader conclusions. % about norm-based and PL-based metrics.
The models we consider have been pretrained on nine datasets.   %, shown in Table~\ref{table:datasets}.
%including ImageNet-1K, and CIFAR-10, CIFAR-100, Street View House Numbers (SVHN), Caltech-UCSD Birds-200-2011 (CUB-200-2011), Pascal VOC2012, ADE20K, Cityscapes, and Common Objects in Context (COCO). 
%%The pretrained models and their accuracy metrics are summarized in the osmr github~\cite{charles-add-link}.
We provide full details about how to reproduce these results in Appendix~\ref{sxn:appendix}.

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
Series        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean) & 0.63 &  0.55 & \textbf{0.64} & \textbf{0.64} \\
$R^{2}$ (std)  & 0.34 &  0.36 & \textbf{0.29} &          0.30 \\
\hline
$MSE$ (mean)   & 4.54 &  9.62 &          3.14 & \textbf{2.92} \\
$MSE$ (std)    & 8.69 & 23.06 &          5.14 & \textbf{5.00} \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average Log Norm and Weighted Alpha metrics across 5 CV datasets, 17 architectures, covering 168 (out of 309) different pretrained DNNs.  
         We include regressions only for architectures with five or more data points, and which are postively correlated with test error.
         These results can be readily reproduced using the Google Colab notebooks (see Appendix~\ref{sxn:appendix}). 
        }
\label{table:results}
\end{table}

### 2020-02-12 submission/appendix.tex
fix typos after full read

Normalization is an important, if underappreciated, practical issue.
Importantly, the normalization of weight matrices does \emph{not} affect the PL fits because $\alpha$ is scale-invariant.
Norm-based metrics, however, do depend strongly on the scale of the weight matrix--that is the point.
%\nred{Indeed, early theoretical work by Bartlett suggests that the test accuracy depends strongly on the ``total size'' of the weight matrics.}
To apply RMT, we usually define $\mathbf{X}$ with $1/N$ normalization, assuming variance of $\sigma^{2}=1.0$.
%\footnote{For Heavy Tailed theorems, one typically needs a normalization such as \nred{$1/N^{\alpha-1}$. check this}}
Pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$, with
 $\sigma^{2}\sim 1/\sqrt{N}$, or some variant, e.g., the Glorot/Xavier normalization~\cite{GloBen10}, or a $\sqrt{2/Nk^2}$ normalization for Convolutional 2D Layers. With this implicit scale, 
we do \emph{not} ``renormalize'' the empirical weight matrices, i.e., we use them as-is.
The only exception is that \emph{we do rescale} the Conv2D pre-activation maps $\mathbf{W}_{i,L}$ 
by $k/\sqrt{2}$ so that they are on the same scale as the Linear / Fully Connected (FC) layers.

@@

NLP models, and other models with large initial embeddings require special care because the
embedding layers frequently lack the implicit $\frac{1}{\sqrt{N}}$ normalization present in other layers.
For example, in GPT, most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$,
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we treat all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $\frac{1}{N}$, or to treat them as an outlier).

@@

\subsection{Reproducing Figure~\ref{fig:resnet204D5L}, Distiller Model}

@@

We attempt to run linear regressions for all pyTorch models for each architecture series for all datasets provided.  
There are over $450$ models in all, and we note that the \texttt{osmr/imgclsmob} repository is constantly being updated with new models.
We omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO, datasets as there are fewer than 15 models for those datasets.  
Also, we filter out regressions with fewer than five datapoints.
The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  78 \\
svhn          &  30 \\
cifar-100     &  30 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used}
\label{table:datasets}
\end{table}`

@@

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical log norm metric against the reported Top 1 (and Top 5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the R-squared and mean squared errors (MSE) for each metric, averaged over all regressions for all architectures and datasets.
Plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & 3.51 & 4.01 \\
 cifar-10 & ResNet  & 0.31 &  0.30 & 0.28 & 0.28 \\
 cifar-100 & ResNet  & 4.13 &  4.50 & 3.06 & 3.06 \\
 svhn & ResNet  & 0.04 &  0.04 & 0.02 & 0.02 \\
 cub-200-2011 & ResNet  & 0.20 &  0.18 & 3.19 & 3.21 \\
 imagenet-1k & EfficientNet  & 9.25 &  9.28 & 9.28 & 9.27 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & 3.59 & 3.71 \\
 imagenet-1k & VGG  & 0.84 &  0.68 & 1.89 & 1.59 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & 18.48 \\
 imagenet-1k & DLA  & 22.41 &  8.49 & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & 0.16 & 0.16 \\
 imagenet-1k & DRN  & 0.60 &  0.66 & 0.40 & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & 13.23 \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & 1.87 & 2.53 \\
 imagenet-1k & ProxylessNAS  & 0.19 &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & 0.07 & 0.08 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & 1.09 \\
 cifar-10 & DIA-ResNet  & 0.05 &  0.08 & 0.28 & 0.32 \\
 cifar-100 & DIA-ResNet  & 0.36 &  1.38 & 0.93 & 1.02 \\
 svhn & DIA-ResNet  & 0.00 &  0.00 & 0.02 & 0.02 \\
 cifar-10 & SENet  & 0.09 &  0.09 & 0.04 & 0.04 \\
 cifar-100 & SENet  & 0.36 &  0.43 & 0.26 & 0.26 \\
 svhn & SENet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 cub-200-2011 & SENet  & 1.07 &  1.29 & 1.85 & 1.95 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & 0.06 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & 0.01 \\
 cifar-100 & ResNeXt  & 0.80 &  0.95 & 0.78 & 0.79 \\
 svhn & ResNeXt  & 0.00 &  0.00 & 0.01 & 0.01 \\
\hline
\end{tabular}
\end{center}
\caption{MSE Results}
\label{table:MSEresults}
\end{table}`

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & 0.90 & 0.88 \\
 cifar-10 & ResNet  & 0.58 &  0.59 & 0.62 & 0.61 \\
 cifar-100 & ResNet  & 0.61 &  0.58 & 0.71 & 0.71 \\
 svhn & ResNet  & 0.69 &  0.70 & 0.82 & 0.81 \\
 cub-200-2011 & ResNet  & 0.94 &  0.95 & 0.08 & 0.08 \\
 imagenet-1k & EfficientNet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & 0.85 & 0.85 \\
 imagenet-1k & VGG  & 0.71 &  0.76 & 0.35 & 0.45 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & 0.81 \\
 imagenet-1k & DLA  & 0.13 &  0.67 & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & 0.97 & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & 0.87 & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & 0.43 \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & 0.92 & 0.89 \\
 imagenet-1k & ProxylessNAS  & 0.68 &  0.56 & 0.53 & 0.58 \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & 0.38 & 0.26 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & 0.99 \\
 cifar-10 & DIA-ResNett  & 0.96 &  0.93 & 0.74 & 0.71 \\
 cifar-100 & DIA-ResNet  & 0.96 &  0.85 & 0.90 & 0.89 \\
 svhn & DIA-ResNet  & 0.94 &  0.95 & 0.78 & 0.77 \\
 cifar-10 & SENet  & 0.91 &  0.91 & 0.96 & 0.96 \\
 cifar-100 & SENet  & 0.97 &  0.96 & 0.98 & 0.98 \\
 svhn & SENet & 0.99 &  0.96 & 0.98 & 0.98 \\
 cub-200-2011 & SENet  & 0.66 &  0.59 & 0.41 & 0.38 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & 0.69 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & 0.21 \\
 cifar-100 & ResNeXt  & 0.17 &  0.02 & 0.20 & 0.18 \\
 svhn & ResNeXt  & 0.87 &  0.90 & 0.64 & 0.75 \\
\hline
\end{tabular}
\end{center}
\caption{$R^{2}$ Results}
\label{table:R2results}
\end{table}`

>>>>

Normalization is an important, if underappreciated, practical issue.
Importantly, the normalization of weight matrices does \emph{not} affect the PL fits because $\alpha$ is scale-invariant.
Norm-based metrics, however, do depend strongly on the scale of the weight matrix---that is the point.
%\nred{Indeed, early theoretical work by Bartlett suggests that the test accuracy depends strongly on the ``total size'' of the weight matrics.}
To apply RMT, we usually define $\mathbf{X}$ with $1/N$ normalization, assuming variance of $\sigma^{2}=1.0$.
%\footnote{For Heavy Tailed theorems, one typically needs a normalization such as \nred{$1/N^{\alpha-1}$. check this}}
Pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$, with
 $\sigma^{2}\sim 1/\sqrt{N}$, or some variant, e.g., the Glorot/Xavier normalization~\cite{GloBen10}, or a $\sqrt{2/Nk^2}$ normalization for Convolutional 2D Layers. With this implicit scale, 
we do \emph{not} ``renormalize'' the empirical weight matrices, i.e., we use them as-is.
The only exception is that \emph{we do rescale} the Conv2D pre-activation maps $\mathbf{W}_{i,L}$ 
by $k/\sqrt{2}$ so that they are on the same scale as the Linear / Fully Connected (FC) layers.

@@

NLP models, and other models with large initial embeddings require special care because the
embedding layers frequently lack the implicit $1/\sqrt{N}$ normalization present in other layers.
For example, in GPT, for most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$,
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we treat all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $1/N$, or to treat them as an outlier).

@@

\subsection{Reproducing Figure~\ref{fig:resnet204D5L}, for the Distiller Model}

@@

We attempt to run linear regressions for all pyTorch models for each architecture series for all datasets provided.  
There are over $450$ models in all, and we note that the \texttt{osmr/imgclsmob} repository is constantly being updated with new models.
We omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO datasets as there are fewer than 15 models for those datasets.  
Also, we filter out regressions with fewer than five datapoints.
The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  78 \\
svhn          &  30 \\
cifar-100     &  30 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used}
\label{table:datasets}
\end{table}

@@

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
Plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & 3.51 & 4.01 \\
 cifar-10 & ResNet  & 0.31 &  0.30 & 0.28 & 0.28 \\
 cifar-100 & ResNet  & 4.13 &  4.50 & 3.06 & 3.06 \\
 svhn & ResNet  & 0.04 &  0.04 & 0.02 & 0.02 \\
 cub-200-2011 & ResNet  & 0.20 &  0.18 & 3.19 & 3.21 \\
 imagenet-1k & EfficientNet  & 9.25 &  9.28 & 9.28 & 9.27 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & 3.59 & 3.71 \\
 imagenet-1k & VGG  & 0.84 &  0.68 & 1.89 & 1.59 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & 18.48 \\
 imagenet-1k & DLA  & 22.41 &  8.49 & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & 0.16 & 0.16 \\
 imagenet-1k & DRN  & 0.60 &  0.66 & 0.40 & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & 13.23 \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & 1.87 & 2.53 \\
 imagenet-1k & ProxylessNAS  & 0.19 &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & 0.07 & 0.08 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & 1.09 \\
 cifar-10 & DIA-ResNet  & 0.05 &  0.08 & 0.28 & 0.32 \\
 cifar-100 & DIA-ResNet  & 0.36 &  1.38 & 0.93 & 1.02 \\
 svhn & DIA-ResNet  & 0.00 &  0.00 & 0.02 & 0.02 \\
 cifar-10 & SENet  & 0.09 &  0.09 & 0.04 & 0.04 \\
 cifar-100 & SENet  & 0.36 &  0.43 & 0.26 & 0.26 \\
 svhn & SENet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 cub-200-2011 & SENet  & 1.07 &  1.29 & 1.85 & 1.95 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & 0.06 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & 0.01 \\
 cifar-100 & ResNeXt  & 0.80 &  0.95 & 0.78 & 0.79 \\
 svhn & ResNeXt  & 0.00 &  0.00 & 0.01 & 0.01 \\
\hline
\end{tabular}
\end{center}
\caption{$MSE$ Results}
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & 0.90 & 0.88 \\
 cifar-10 & ResNet  & 0.58 &  0.59 & 0.62 & 0.61 \\
 cifar-100 & ResNet  & 0.61 &  0.58 & 0.71 & 0.71 \\
 svhn & ResNet  & 0.69 &  0.70 & 0.82 & 0.81 \\
 cub-200-2011 & ResNet  & 0.94 &  0.95 & 0.08 & 0.08 \\
 imagenet-1k & EfficientNet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & 0.85 & 0.85 \\
 imagenet-1k & VGG  & 0.71 &  0.76 & 0.35 & 0.45 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & 0.81 \\
 imagenet-1k & DLA  & 0.13 &  0.67 & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & 0.97 & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & 0.87 & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & 0.43 \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & 0.92 & 0.89 \\
 imagenet-1k & ProxylessNAS  & 0.68 &  0.56 & 0.53 & 0.58 \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & 0.38 & 0.26 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & 0.99 \\
 cifar-10 & DIA-ResNett  & 0.96 &  0.93 & 0.74 & 0.71 \\
 cifar-100 & DIA-ResNet  & 0.96 &  0.85 & 0.90 & 0.89 \\
 svhn & DIA-ResNet  & 0.94 &  0.95 & 0.78 & 0.77 \\
 cifar-10 & SENet  & 0.91 &  0.91 & 0.96 & 0.96 \\
 cifar-100 & SENet  & 0.97 &  0.96 & 0.98 & 0.98 \\
 svhn & SENet & 0.99 &  0.96 & 0.98 & 0.98 \\
 cub-200-2011 & SENet  & 0.66 &  0.59 & 0.41 & 0.38 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & 0.69 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & 0.21 \\
 cifar-100 & ResNeXt  & 0.17 &  0.02 & 0.20 & 0.18 \\
 svhn & ResNeXt  & 0.87 &  0.90 & 0.64 & 0.75 \\
\hline
\end{tabular}
\end{center}
\caption{$R^{2}$ Results}
\label{table:R2results}
\end{table}

### 2020-02-12 submission/conclusion.tex
fix typos after full read

\ncyan{
We conclude with a few thoughts on what a \emph{practical theory} of DNNs should look like.
\michael{MM TO DO.}
%
We distinguish between what we will call a
\emph{phenomenological theory}
(that describes empirical relationship of phenomena to each other, in a way which is consistent with fundamental theory, but is not directly derived from that theory)
and what can be called a 
\emph{first principles theory} 
(that is applicable to toy models, but that does not scale up to realistic systems if one includes realistic apsects of realistic systems).
%
For most complex highly-engineered systems (aside from complex AI/ML systems), one \emph{uses} phenomenological theory rather than first principles theory. 
(One does not try to solve the Schr\"odinger equation if one is interested in building a bridge or flying an airplane.)
%
Our results, which are based on our \emph{use} of sophisticated statistical mechanics theory to solve an important practical DNN problems, suggests that this approach should be of interest more generally for those interested in developing a practical DNN theory.
%\charles{it is the oppposite...ab initio theory scales quite well...it is the spherical cow models of physics and ML that do not scale. What we have is a semi-empirical theory.  We use real theory, but require empirical input, at least in the new stat mech work.  What we have introduced is a phenomenology, which to me is different from a semi-empirical or phenomenological theory  }
}

>>>>

\ncyan{
We conclude with a few thoughts on what a \emph{practical theory} of DNNs should look like.

To do so, we distinguish between two types of theories:
what may be called an \emph{non-empirical or analogical theory}, in which one creates a very simple model that can be analyzed rigorously, and one argues that the model has properties that are analogous the the system of interest; and 
what may be called a \emph{semi-empirical theory}, in which there exists a rigorous asymptotic theory that has asymptotic parameters, and one adjusts or fits the parameters to the finite data.

often one simple enough to perform ``rigorous'' analysis, and one argues that although simple

%\michael{MM TO DO.}
%%
%We distinguish between what we will call a
%\emph{phenomenological theory}
%(that describes empirical relationship of phenomena to each other, in a way which is consistent with fundamental theory, but is not directly derived from that theory)
%and what can be called a 
%\emph{first principles theory} 
%(that is applicable to toy models, but that does not scale up to realistic systems if one includes realistic apsects of realistic systems).
%%
%For most complex highly-engineered systems (aside from complex AI/ML systems), one \emph{uses} phenomenological theory rather than first principles theory. 
%(One does not try to solve the Schr\"odinger equation if one is interested in building a bridge or flying an airplane.)
%%

Much of the work on the theory of DNNs focuses on the former type of theory, but our approach is of the latter type.
Our results, however, which are based on our \emph{use} of sophisticated statistical mechanics theory to solve an important practical DNN problems, suggests that our approach should be of interest more generally for those interested in developing a practical DNN theory.
}
